---
title: "07_delay_unit_by_age"
author: "Kendra Seaman"
date: "6/4/2020"
output: html_document
---

```{r setup, include=FALSE, cache= FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
source("../07_graph_by_delay_unit.R")
m1 <- readRDS("../output/model1.RDS")
younger <- readRDS("../output/youngerttest.RDS")
older <- readRDS("../output/olderttest.RDS")
```

## Proportion of Smaller, Sooner Choices by Delay and Age

```{r Delay Unit by Kval, echo = FALSE}
graph_delay_unit_age
```

```{r model, echo = FALSE}
m1$ANOVA %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:3, bold =T, background = 'yellow')
```

There is main effect of age (which varied between-subjects) with older adults choosing the smaller, sooner option less. 

```{r sphericity, echo = FALSE}
m1$`Mauchly's Test for Sphericity` %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:2, bold =T, background = 'yellow')
```

Mauchley's test was significant for all within-subject variable, so use the GGe corrected values below:

```{r correction, echo = FALSE}
m1$`Sphericity Corrections` %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:2, bold = T, background = 'yellow')
```

### Follow-up T-tests within age groups
### Younger
T-Value followed by p value
```{r young, echo = FALSE}
younger$tval %>%
  kable() %>%
  kable_styling() 

younger$`p value` %>%
  kable() %>%
  kable_styling() 
```

### Older
T-Value followed by p value
```{r old, echo = FALSE}
older$tval %>%
  kable() %>%
  kable_styling() 

older$`p value` %>%
  kable() %>%
  kable_styling() 
```