---
title: "Graphing Choice by Delay Unit"
author: "Shelby Leverett"
date: "4/16/2020"
output: html_document
---

```{r setup, include=FALSE, cache= FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
source("../07_graph_by_delay_unit.R")
m1 <- readRDS("../output/model1.RDS")
```

## *Proportion of Sooner Choice by Unit of Delay & Kval*

```{r Delay Unit by Kval, echo = FALSE}
graph_delay_unit_kval
```

```{r model, echo = FALSE}
m1$ANOVA %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1, bold =T, background = 'yellow')
```

There is main effect of age (which varied between-subjects) with older adults choosing the smaller, sooner option less. 

```{r sphericity, echo = FALSE}
m1$`Mauchly's Test for Sphericity` %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:6, bold =T, background = 'yellow')
```

Mauchley's test was significant for all within-subject variable, so use the GGe corrected values below:

```{r correction, echo = FALSE}
m1$`Sphericity Corrections` %>%
  kable() %>%
  kable_styling() %>%
  row_spec(1:6, bold = T, background = 'yellow')
```

Main effect of kvalue: smaller kvalues equal more discounting.
Main effect of delay: longer delays equal less discounting
Interactions between kvalue and delay: smaller kvalues (005, 05) show declines in discounting with longer delays while larger kvalues (1) show no differnces in discounting across different delays (follow-up paired comparisons needed) 

## *Proportion of Sooner Options by Delay Unit, Kval, and Age*

```{r Delay Unit by Kval & Age, echo = FALSE, fig.height = 10}
graph_delay_unit_kval_age
```

