---
title: "10_exploratory_analyses"
author: "Shelby Leverett"
date: "6/26/2020"
output: html_document
---

```{r setup, include=FALSE, cache= FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(kableExtra)
source("../10_exploratory_analyses.R")
source("../09_graph_framing_effect.R")
source("../06_framing_effect_model.R")
```

# Correlations Between Age, FTP, and Savings & Safety Nets

```{r correlation matrix, echo = FALSE, comment=''}
as.data.frame(cor_table$r)[1]
```
p values
```{r correlation matrix2, echo = FALSE, comment=''}
as.data.frame(cor_table$P)[1]
```
There is significant negative correlation between Age & FTP, so as age increases, time horizons decrease. 
There is also a significant negative correlation between Age and Health Insurance. As age increases, health insurance coverage increases (for health_ins: 1=Yes, 2=No).
There is a slight positive correlation between Age and Liquid Savings (r=.11, p=.06)

- FTP: higher scores = longer time horizions
- health_ins: 1=Yes, 2= No --> so lower health_ins scores means more insurance

# Does FTP mediate the relationship between age and choice?

For the trials where the effect of age  on discounting behavior is strongest (i.e: delay=10 years), is this effect mediated by FTP?

## Step 1: Age --> FTP

```{r age on ftp, echo=FALSE}
summary(step1)
```
FTP significantly predicts age (B= -.02, p=.000)

## Step 2: FTP --> Choice
```{r ftp on choice, echo = FALSE}
summary(step2)
```
FTP does not predict choice (B= -.003, p=.82)

## Step 3: FTP + AGE --> Choice
```{r ftp+age on choice, echo=FALSE}
summary(step3)
```

FTP does not mediate the relationship between age and choice.

# Framing Effects

## *1 week vs 7 days*

```{r 1 week vs 7 days, echo = FALSE}
oneweek_vs_7days
```

## *1 month vs 4 weeks*

```{r One month vs Four Weeks, echo = FALSE}
onemonth_vs_4weeks
```

## *1 year vs 12 months*

```{r 1 year vs 12 months, echo = FALSE}
oneyear_vs_12months
```

```{r Framing Model Summary M3, echo=FALSE}
summary(M3)
```

Controlling for age, frame was only significant for one out of three levels. Framing the delay as "4 weeks" instead of "1 month" increased discounting (maybe run a t-test here?!). The other frames (i.e: 12 months vs 1 year, and 7 days vs 1 week) had no significant effect on discounting.